

    %=====================================
    %   WARNING
    %   FICHIER AUTOMATISE
    %   NE PAS MODIFIER
    %=====================================

    \newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Papier 35
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Indexations
\index{GetieMuluken@Getie, Muluken}
\index{LanzettaFrancois@Lanzetta, François}
\index{BegotSylvie@Bégot, Sylvie}
\index{AdmassuBimrewT.@Admassu, Bimrew T.}
%
% Titre
\begin{flushleft}
\phantomsection\addtocounter{section}{1}
\addcontentsline{toc}{section}{Loss effect analysis of irreversible Stirling cycle refrigerator}
{\Large \textbf{Loss effect analysis of irreversible Stirling cycle refrigerator}}\label{ref:35}
\end{flushleft}
%
% Auteurs
Muluken Z. Getie$^{1,\star}$, François Lanzetta$^{2}$, Sylvie Bégot$^{2}$, Bimrew T. Admassu$^{3}$\\[2mm]
$^{\star}$ \Letter : \url{muluken.zegeye@bdu.edu.et}\\[2mm]
{\footnotesize $^{1}$ 1.  FEMTO-ST Institute, Univ. Bourgogne Franche-Comte, CNRS Parc technologique, 2 avenue Jean Moulin, F-90000 Belfort, France            2. Bahir Dar Energy Center, Bahir Dar Institute of Technology, Bahir Dar University, Bahir Dar, Ethiopia           3.}\\
{\footnotesize $^{2}$ FEMTO-ST Institute, Univ. Bourgogne Franche-Comte, CNRS Parc technologique, 2 avenue Jean Moulin, F-90000 Belfort, France}\\
{\footnotesize $^{3}$ Faculty of Mechanical and Industrial Engineering, Bahir Dar Institute of Technology, Bahir Dar University, Bahir Dar, Ethiopia}\\
[4mm]
%
% Mots clés
\noindent \textbf{Mots clés : } Stirling refrigerator, Power losses, Heat losses, Performance, Share of losses\\[4mm]
%
% Résumé
\noindent \textbf{Résumé : } 

{\normalsize
This paper demonstrates the share of different power and heat losses on the total losses of the respective categories of a Stirling machine. The design and development of Stirling cycle refrigerators require an understanding of the processes that govern the operation of the machine.  The operating condition and processes of the Stirling cycle refrigerator are accompanied by different types of losses. Power losses (including losses due to fluid friction, mechanical friction, finite speed, and gas hysteresis)  tend to increase the input power requirement and heat losses( including losses due to shuttle heat, regenerator ineffectiveness, and conduction heat) that tend to decrease the amount of cooling. Different losses have been evaluated for the modified simple model using the geometrical parameters of the FEMTO--ST engine model. The share of major power and heat losses have been presented at a particular working condition. The major power and heat losses, as well as their effect on the performance of the cooling machine, have been discussed. The biggest power loss is loss due to fluid friction followed by mechanical friction loss. At a pressure of 17.5 bar, these two types of losses contribute about 94\% of the total power loss. The major heat loss is loss due to regenerator ineffectiveness. Furthermore, the share of different power and heat losses for different rotational speeds have been studied as well as their effects on the performance of the cooling machine have been discussed. The share of fluid friction loss and loss due to regenerator ineffectiveness increase with rotational speed. The coefficient of performance of the refrigerating machine decrease with the rising rotational speed majorly due to the increase of fluid friction and regenerator ineffectiveness losses. Hence, the design of the Stirling refrigerator shall consider the operating range of the machine so that critical investigation could be done to minimize major losses.  On the other hand, the share of heat loss is majorly dependent on the temperature gradient between the hot and cold reservoirs. This is because heat conduction loss is majorly affected by temperature difference.

 \vfill doi : \url{https://doi.org/10.25855/SFT2021-035}

}
 
